Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-02-12 paper.tex
One more significant contribution from Marina Karsanina

Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}) \cite{dimitrakopoulos2010high}. Thus, the
output has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of
the input array along selected axes. Note that shift operators with such $x_1$ and $x_2$
represent a 3-point function computed within a 3D domain, but along a predefined direction (see below).
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{images/pattern.png}
  \caption[]{The pattern used for calculation of $S_3$ function in our
    implementation. Vectors $x_1$ and $x_2$ are parallel to one of the axes $X$,
    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively. A red triangle
    contributes to $S_3(2, 6)$ and blue triangles contribute to $S_3(1, 1)$.}
  \label{fig:pattern}
\end{figure}

>>>>

Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}) \cite{dimitrakopoulos2010high}. Thus, the
output has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of
the input array along selected axes. Note that shift operators with such $x_1$ and $x_2$
represent a 3-point function computed within a 3D domain, but along a predefined direction (see below).
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{images/pattern.png}
  \caption[]{The pattern used for calculation of $S_3$ function in our
    implementation.}
  \label{fig:pattern}
\end{figure}
